\section{OWASP}
\subsubsection{Injection}
Occur when untrusted data is sent to an interpreter as part of a command or query.

\subsubsection{Broken Authentication}
Application functions related to authentication and session management are often implemented incorrectly, allowing attackers to compromise passwords, keys, or session tokens, or to exploit other implementation flaws to assume other users’ identities.

\subsubsection{Sensitive Data Exposure}
Many web applications and APIs do not properly protect sensitive data, such as financial, healthcare, and PII. Attackers may steal or modify such weakly protected data.

\subsubsection{XML External Entities}
Many older or poorly configured XML processors evaluate external entity references within XML documents. External entities can be used to disclose internal files using the file URI handler, internal file shares, internal port scanning, remote code execution, and DoS attacks.

\subsubsection{Broken Access Control}
Restrictions on what authenticated users are allowed to do are often not properly enforced.

\subsubsection{Security Misconfiguration}
een issue. This is commonly a result of insecure default configurations, incomplete or ad hoc configurations, open cloud storage, misconfigured HTTP headers, and verbose error messages containing sensitive information.

\subsubsection{XSS}
XSS flaws occur whenever an application includes untrusted data in a new web page without proper validation or escaping, or updates an existing web page with user-supplied data using a browser API that can create HTML or JavaScript. XSS allows attackers to execute scripts in the victim’s browser which can hijack user sessions, deface web sites, or redirect the user to malicious sites.

\subsubsection{Insecure Deserialization}
Insecure deserialization often leads to remote code execution.

\subsubsection{Components with Vulnerabilities}
Components, such as libraries, frameworks, and other software modules, run with the same privileges as the application. If a vulnerable component is exploited, such an attack can facilitate serious data loss or server takeover.

\subsubsection{Insufficient Logging \& Monitoring}
Insufficient logging and monitoring, coupled with missing or ineffective integration with incident response, allows attackers to further attack systems, maintain persistence, pivot to more systems, and tamper, extract, or destroy data.
